Inferring stellar rotation periods with Gaussian processes

### 2016-11-01 documents/ms.tex

\documentclass[useAMS, usenatbib, preprint, 12pt]{aastex}
\usepackage{cite, natbib}
% \documentclass[onecolumn, 12pt, usenatbib, preprint]{emulateapj}
\usepackage{float}
\usepackage{epsfig}
\usepackage{cases}
\usepackage[section]{placeins}
\usepackage{graphicx, subfigure}
\usepackage{color}

\newcommand{\article}{article}
\newcommand{\oxford}{1}
\newcommand{\uw}{2}
\newcommand{\sagan}{3}
\newcommand{\ktwo}{{\it K2}}
\newcommand{\eg}{{\it e.g.}}
\newcommand{\ie}{{\it i.e.}}
\newcommand{\nlightcurves}{300}
\newcommand{\Kepler}{{\it Kepler}}
\newcommand{\kepler}{\Kepler}

@@

\title{Stellar rotation period inference with Gaussian processes}

\author{%
   Ruth Angus\altaffilmark{\oxford}
   Suzanne Aigrain\altaffilmark{\oxford}
   \& Daniel Foreman-Mackey\altaffilmark{\uw}\altaffilmark{\sagan}
}

\altaffiltext{\oxford}{Subdepartment of Astrophysics, University of Oxford,
OX1 3RH, UK}
\altaffiltext{\uw}{Department of Astronomy, University of Washington, Seattle,
WA, USA}
\altaffiltext{\sagan}{Sagan fellow}

@@

% \begin{figure}
% \begin{center}
% \includegraphics[width=6in, clip=true]{figures/Kepler452b.pdf}
% \caption[A light curve with a GP model.]
% {Light curve of Kepler-452 b, a habitable-zone, Earth-sized planet
% hosting G star \citep{Jenkins2015}. The orange line shows a fit to the data using
% a Gaussian process model with a QP covariance kernel function.}
% \label{fig:GP_example}
% \end{center}
% \end{figure}

@@

The data presented in this paper were obtained from the Mikulski Archive for
Space Telescopes (MAST).
STScI is operated by the Association of Universities for Research in Astronomy,
Inc., under NASA contract NAS5-26555.
Support for MAST for non-HST data is provided by the NASA Office of Space
Science via grant NNX09AF08G and by other grants and contracts.
This paper includes data collected by the Kepler mission.
Funding for the Kepler mission is provided by the NASA Science Mission
directorate.

\bibliographystyle{plainnat}
\bibliography{GProtation}

\end{document}

>>>>

\documentclass[useAMS, usenatbib, preprint, 12pt]{aastex}
\usepackage{cite, natbib}
\usepackage{float}
\usepackage{epsfig}
\usepackage{cases}
\usepackage[section]{placeins}
\usepackage{graphicx, subfigure}
\usepackage{color}

\newcommand{\columbia}{1}
\newcommand{\oxford}{2}
\newcommand{\uw}{3}
\newcommand{\nlightcurves}{333}
\newcommand{\Kepler}{{\it Kepler}}
\newcommand{\kepler}{\Kepler}
\newcommand{\corot}{{\it CoRoT}}
\newcommand{\Ktwo}{{\it K2}}
\newcommand{\ktwo}{\Ktwo}
\newcommand{\TESS}{{\it TESS}}
\newcommand{\LSST}{{\it LSST}}
\newcommand{\SDSS}{{\it SDSS}}
\newcommand{\PLATO}{{\it PLATO}}
\newcommand{\Teff}{$T_{\mathrm{eff}}$}
\newcommand{\teff}{$T_{\mathrm{eff}}$}
\newcommand{\FeH}{[Fe/H]}
\newcommand{\feh}{[Fe/H]}
\newcommand{\ie}{{\it i.e.}}
\newcommand{\eg}{{\it e.g.}}
\newcommand{\logg}{log \emph{g}}
\newcommand{\dnu}{$\Delta \nu$}
\newcommand{\numax}{$\nu_{\mathrm{max}}$}

@@

\title{Inferring stellar rotation periods with Gaussian processes}

\author{%
   Ruth Angus\altaffilmark{\columbia}
   Suzanne Aigrain\altaffilmark{\oxford}
   \& Daniel Foreman-Mackey\altaffilmark{\uw}
}

\altaffiltext{\columbia}{Simons Fellow, Columbia University, NY, NY,
ruthangus@gmail.com}
\altaffiltext{\oxford}{Subdepartment of Astrophysics, University of Oxford,
OX1 3RH, UK}
\altaffiltext{\uw}{Department of Astronomy, University of Washington, Seattle,
WA}

@@

@@

% acknowledgements

\bibliographystyle{plainnat}
\bibliography{GProtation}
\end{document}
